The Astropy Project: xx

### 2021-12-01 src/ms.tex
intro first bits

Over the last decade, \python has grown enormously in popularity to become a
dominant programming language in the astronomical (and broader) scientific
community.
For example, Figure~\ref{fig:python-mentions} shows the number of yearly
full-text mentions of \python as compared to a few other programming languages
in refereed articles in the astronomical literature, demonstrating its nearly
exponential growth in popularity.
The rapid adoption of \python by astronomy researchers, students, observatories,
and technical staff combined with an associated increase in awareness and
interest about open-source software tools is leading a paradigm shift in the way
research is done, data is analyzed, and results are shared.

@@

A major reason that Python has been adopted in the sciences is the huge amount
of community-oriented, open-source software tools that are available to
anyone...TODO.
TODO: Numpy, scipy, matplotlib, scientific software ecosystem.
In astronomy, one of the first large, community-oriented, open-source \python packages ... was Astropy ... (note: yt)
TODO: words about astropy core package.
TODO: The core package is now largely stable and provides core foundational tools.
TODO: Astropy has expanded to become the Astropy Project: Broader scope than core package. Core package, Ecosystem of tools, Community of users, developers, maintainers

>>>>

The \python programming language is a high-level, interpreted (versus compiled)
programming language that has become an industry standard across many
computational domains, technological sectors, and fields of research.
Despite claims to the contrary \citep{Portegies-Zwart:2020}, \python enables
scalable, time- and energy-efficient code execution \citep[e.g.,][]{Augier:2021}
with a focus on code readability, ease of use, and interoperability with other
languages.
Over the last decade, \python has grown enormously in popularity to become a
dominant programming language in the astronomical and broader scientific
communities.
For example, Figure~\ref{fig:python-mentions} shows the number of yearly
full-text mentions of \python as compared to a few other programming languages
in refereed articles in the astronomical literature, demonstrating its nearly
exponential growth in popularity.
The rapid adoption of \python by astronomy researchers, students, observatories,
and technical staff combined with an associated increase in awareness and
interest about open-source software tools is contributing to a paradigm shift in
the way research is done, data is analyzed, and results are shared in astronomy
and beyond.

One of the factors that has led to its rapid ascent in popularity in scientific
contexts has been significant volunteer-driven effort behind developing
community-oriented open-source software tools and fostering communities of users
and developers that have grown around these packages.
TODO: Numpy, scipy, matplotlib, scientific software ecosystem.
The astropy core package ... one of the first large, community-oriented, open-source \python packages ... was Astropy ... (note: yt)
TODO: words about astropy core package.
TODO: The core package is now largely stable and provides core foundational tools.

TODO: Astropy has expanded to become the Astropy Project: Broader scope than core package. Core package, Ecosystem of tools, Community of users, developers, maintainers

@@
